---
title: "Indian Food Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(tidyverse)
library(DT)
options(knitr.table.format = "html")
```

```{r}

library(tidyverse)

indian_food <- read.csv("indian_food.csv")

# splitting the ingredients into rows to make the data tidy for future analysis 

indian_food_tidy <-  indian_food %>% # this will only be used to analyze any ingredients related data
   mutate(ingredients = strsplit(as.character(ingredients), ", ")) %>% 
   unnest(ingredients)


# removing -1 values from the data into NA values 


indian_food[ indian_food == -1 ] <- NA # removing -1 values into NA in both tables
indian_food_tidy[ indian_food_tidy == -1 ] <- NA # removing -1 values into NA

```
\# what is the most common diet in indian food? \
```{r}
tail(names(sort(table(indian_food$diet))), 1) # i found this online i have no idea how it works
```
\# what is the most common ingredients? \
```{r}
tail(names(sort(table(indian_food_tidy$ingredients))), 1)
```
\# what is the average perp time? \
```{r}
indian_food %>% 
  summarise(avg_prep_time =mean(prep_time , na.rm = TRUE)) # why it did not work without summarise ??
```
\# what is the average cooking time? \
```{r}
indian_food %>% 
  summarise( avg_cook_time = mean( cook_time , na.rm = TRUE ))
```
\# average cooking time total time (perp+cook)\
```{r}
indian_food %>% 
  summarise( avg_total_cooking_time = mean( cook_time , na.rm = TRUE ) + mean(prep_time , na.rm = TRUE) )
```
\# range of prep time\ 

```{r}
indian_food %>% 
  summarise(range_prep_time = range(prep_time, na.rm = TRUE))%>% 
  datatable() # what is the difference if i assigned it to variable such as r=
```


\# range of cooking time\

```{r}
indian_food %>% 
  summarise(range_cook_time =range(cook_time, na.rm = TRUE))%>% 
  datatable()
```


\# what is the most common course type?\

```{r}
tail(names(sort(table(indian_food$course))), 1)
```


\# what is the most common flavor profile?\

```{r}
tail(names(sort(table(indian_food$flavor_profile))), 1)
```


\#what is the most common ingredients in a course type?\

```{r}
indian_food_tidy %>% 
  group_by(course) %>%
 summarise( tail(names(sort(table(ingredients))), 1)) %>% 
  datatable() # mode not working here
```
 

\#what is the most common ingredients in a flavor type?\

```{r}
indian_food_tidy %>% 
  group_by(flavor_profile) %>%
  summarise( tail(names(sort(table(ingredients))), 1))%>% 
  datatable()
```


\#what is the most common course in a state/region?\
\# state\

```{r}
indian_food %>% 
  group_by(state) %>%
  summarise( tail(names(sort(table(course))), 1))%>% 
  datatable()
```


\# region\

```{r}
indian_food %>% # there is a region with no value how we can remove it 
  group_by(region) %>%
  summarise( tail(names(sort(table(course))), 1))%>% 
  datatable()
```


\#what is the most common ingredients in a state/region?\
\# state\

```{r}
indian_food_tidy %>% 
  group_by(state) %>%
  summarise( tail(names(sort(table(ingredients))), 1))%>% 
  datatable()
```


\# region\

```{r}
indian_food_tidy %>% 
  group_by(region) %>%
  summarise( tail(names(sort(table(ingredients))), 1))%>% 
  datatable()
```


\#what is the most common flavor type in a state/region?\
\# state\

```{r}
indian_food %>% 
  group_by(state) %>%
  summarise( tail(names(sort(table(flavor_profile))), 1))%>% 
  datatable()
```


\# region\

```{r}
indian_food %>% 
  group_by(region) %>%
  summarise( tail(names(sort(table(flavor_profile))), 1))%>% 
  datatable()
```


\#what is the most common diet in a state/region?\
\# state\

```{r}
indian_food %>% 
  group_by(state) %>%
  summarise(s1= tail(names(sort(table(diet))), 1))%>% 
  datatable()
```


\# reigon\

```{r}
indian_food %>% 
  group_by(region) %>%
  summarise( tail(names(sort(table(diet))), 1))%>% 
  datatable()
```


\#what is the average prep time / cooking time in a state/region?\
\# prep time / state\

```{r}
indian_food %>% 
  group_by(state) %>% 
  summarise(avg = mean(prep_time, na.rm = TRUE)) %>% 
  datatable()#%>% 
#slice_max(1) # if i want to find the top but it is not working
```
 

\# prep time / region\

```{r}
indian_food %>% 
  group_by(region) %>% 
  summarise(avg = mean(prep_time, na.rm = TRUE)) %>% 
  datatable()# %>% 
  #slice_max(1) # to find the min but it is not working too
```
 

\# cooking time / state \

```{r}
indian_food %>% 
  group_by(state) %>% 
  summarise(avg = mean(cook_time, na.rm = TRUE)) %>% 
datatable()
```


\# cooking time / region\

```{r}
indian_food %>% 
  group_by(region) %>% 
  summarise(avg = mean(cook_time, na.rm = TRUE))%>% 
  datatable()
```


\# the region which has the highest number of dishes \

```{r}
tail(names(sort(table(indian_food$region))), 1)
```

\# the state which has the highest number of dishes\ 

```{r}
tail(names(sort(table(indian_food$state))), 1)

```

\# points plots describing cooking time by prep time\

```{r}
indian_food %>% 
  ggplot(aes(x= prep_time, y=cook_time))+ 
  geom_point()+
  theme(aspect.ratio = 1,
        axis.line = element_blank())+
  coord_cartesian(xlim = c(0,300), ylim = c(0,125), expand = 0, clip = "off")
```

